Chapter 4

### 2021-08-04 thesis_chapter_4.Rmd
started to read data in

houtbay <- tidync("OceanParcels/trajectory_data/chapter_4_output/houtbay.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

houtbay_mean <- houtbay %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

houtbay$site <- "Hout Bay" 
houtbay_mean$site <- "Hout Bay"

kommetjie <- tidync("OceanParcels/trajectory_data/chapter_4_output/kommetjie.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

kommetjie_mean <- kommetjie %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

kommetjie$site <- "kommetjie" 
kommetjie_mean$site <- "kommetjie"

soetwater <- tidync("OceanParcels/trajectory_data/chapter_4_output/soetwater.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

soetwater_mean <- soetwater %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

soetwater$site <- "Soetwater" 
soetwater_mean$site <- "Soetwater"

millers <- tidync("OceanParcels/trajectory_data/chapter_4_output/millers.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2020-01-01 00:00:00"))

millers_mean <- millers %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

millers$site <- "millers" 
millers_mean$site <- "millers"

total_data <- rbind(houtbay, soetwater, kommetjie, millers)
total_data_mean <- rbind(houtbay_mean, soetwater_mean,kommetjie_mean, millers_mean)
```

@@

```{r eval = FALSE, message=FALSE, warning=FALSE, echo=FALSE}

library(ggplot2)

## Coastline of Southern Africa
load("map/south_africa_coast_hi_res.Rdata")

mean_traj_site <- ggplot() + 
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_path(data = total_data_mean, aes(x = lon, y = lat, colour = site)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

```{r eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE}

mean_traj_site

## Density comparisons

```{r eval = FALSE, message=FALSE, echo=FALSE, warning=FALSE}

## Coastline of Southern Africa
load("map/south_africa_coast_hi_res.Rdata")

heatmap_houtbay <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  geom_hex(data = houtbay, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = houtbay_mean,aes(x = lon, y = lat, color = 'red'),             show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("HoutBay") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_komm <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kommetjie, bins = 80, aes(x = lon, y = lat), legend = FALSE) +   scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = kommetjie_mean,aes(x = lon, y = lat, color = 'red'),           show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Kommetjie") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_soetwater <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = soetwater, bins = 80, aes(x = lon, y = lat), legend = FALSE) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = soetwater_mean,aes(x = lon, y = lat, color = 'red'),           show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Soetwater") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_soetwater <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = soetwater, bins = 80, aes(x = lon, y = lat), legend = FALSE) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = soetwater_mean,aes(x = lon, y = lat, color = 'red'),           show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Kommetjie") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_millers <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = millers, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000000)) +
  geom_path(data = millers_mean,aes(x = lon, y = lat, color = 'red'),             show.legend = FALSE) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Millers") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```{r , eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE}

ggarrange(heatmap_houtbay, heatmap_soetwater, heatmap_millers, ncol = 1, nrow = 3, font.label = list(size = 11, face = "bold"), common.legend = FALSE, legend = c("bottom"), labels = "AUTO", align = "hv")
```

```{r total heatmap, eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE}

heatmap_total <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group =    PID), size =    1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = total_data, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 19000000)) +
  geom_path(data = total_data_mean,aes(x = lon, y = lat, color = 'red'),show.legend = FALSE) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=10, xmax=18.4, ymin=-33, ymax=-33.5),           inherit.aes = FALSE, fill = NA, colour =    "red", size = 1.5) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=10, xmax=18.4, ymin=-33.5, ymax=-34.0),           inherit.aes = FALSE, fill = NA, colour =    "green", size = 1.5) +
  geom_rect(data = south_africa_coast_hi_res,aes(xmin=10, xmax=18.4, ymin=-34.0, ymax=-34.5),           inherit.aes = FALSE, fill = NA, colour =    "black", size = 1.5) +
  #coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Millers") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
heatmap_total
```

>>>>

houtbay_summer <- tidync("OceanParcels/chapter_4_output/hb_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
houtbay_summer$season <- "Summer" 
houtbay_summer$site <- "Hout Bay" 
houtbay_summer_mean <- houtbay_summer %>% # calculate mean trajectory
 group_by(t) %>% 
 summarise(across(lon:bathy, mean, na.rm= TRUE))
houtbay_summer_mean$season <- "Summer" 
houtbay_summer_mean$site <- "Hout Bay"

houtbay_autumn <- tidync("OceanParcels/chapter_4_output/hb_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
houtbay_autumn$season <- "Autumn" 
houtbay_autumn$site <- "Hout Bay" 
houtbay_autumn_mean <- houtbay_autumn %>% # calculate mean trajectory
 group_by(t) %>% 
 summarise(across(lon:bathy, mean, na.rm= TRUE))
houtbay_autumn_mean$season <- "Autumn" 
houtbay_autumn_mean$site <- "Hout Bay"

houtbay_winter <- tidync("OceanParcels/chapter_4_output/hb_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
houtbay_winter$season <- "Winter" 
houtbay_winter$site <- "Hout Bay" 
houtbay_winter_mean <- houtbay_winter %>% # calculate mean trajectory
 group_by(t) %>% 
 summarise(across(lon:bathy, mean, na.rm= TRUE))
houtbay_winter_mean$season <- "Winter" 
houtbay_winter_mean$site <- "Hout Bay"

houtbay_spring <- tidync("OceanParcels/chapter_4_output/hb_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
houtbay_spring$season <- "Spring" 
houtbay_spring$site <- "Hout Bay" 
houtbay_spring_mean <- houtbay_spring %>% # calculate mean trajectory
 group_by(t) %>% 
 summarise(across(lon:bathy, mean, na.rm= TRUE))
houtbay_spring_mean$season <- "Spring" 
houtbay_spring_mean$site <- "Hout Bay"

kom_summer <- tidync("OceanParcels/chapter_4_output/kom_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kom_summer$season <- "Summer" 
kom_summer$site <- "Kommetjie" 
kom_summer_mean <- kom_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kom_summer_mean$season <- "Summer" 
kom_summer_mean$site <- "Kommetjie"

kom_autumn <- tidync("OceanParcels/chapter_4_output/kom_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kom_autumn$season <- "Autumn" 
kom_autumn$site <- "Kommetjie" 
kom_autumn_mean <- kom_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kom_autumn_mean$season <- "Autumn" 
kom_autumn_mean$site <- "Kommetjie"

kom_winter <- tidync("OceanParcels/chapter_4_output/kom_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kom_winter$season <- "Winter" 
kom_winter$site <- "Kommetjie" 
kom_winter_mean <- kom_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kom_winter_mean$season <- "Winter" 
kom_winter_mean$site <- "Kommetjie"

kom_spring <- tidync("OceanParcels/chapter_4_output/kom_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kom_spring$season <- "Spring" 
kom_spring$site <- "Kommetjie" 
kom_spring_mean <- kom_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kom_spring_mean$season <- "Spring" 
kom_spring_mean$site <- "Kommetjie"

scar_summer <- tidync("OceanParcels/chapter_4_output/scar_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
scar_summer$season <- "Summer" 
scar_summer$site <- "Scarborough" 
scar_summer_mean <- scar_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
scar_summer_mean$season <- "Summer" 
scar_summer_mean$site <- "Scarborough"

scar_autumn <- tidync("OceanParcels/chapter_4_output/scar_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
scar_autumn$season <- "Autumn" 
scar_autumn$site <- "Scarborough" 
scar_autumn_mean <- scar_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
scar_autumn_mean$season <- "Autumn" 
scar_autumn_mean$site <- "Scarborough"

scar_winter <- tidync("OceanParcels/chapter_4_output/scar_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
scar_winter$season <- "Winter" 
scar_winter$site <- "Scarborough" 
scar_winter_mean <- scar_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
scar_winter_mean$season <- "Winter" 
scar_winter_mean$site <- "Scarborough"

scar_spring <- tidync("OceanParcels/chapter_4_output/scar_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
scar_spring$season <- "Spring" 
scar_spring$site <- "Scarborough" 
scar_spring_mean <- scar_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
scar_spring_mean$season <- "Spring" 
scar_spring_mean$site <- "Scarborough"

oude_summer <- tidync("OceanParcels/chapter_4_output/oudekraal_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_summer$season <- "Summer" 
oude_summer$site <- "Oudekraal" 
oude_summer_mean <- oude_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_summer_mean$season <- "Summer" 
oude_summer_mean$site <- "Oudekraal"

oude_autumn <- tidync("OceanParcels/chapter_4_output/oudekraal_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_autumn$season <- "Autumn" 
oude_autumn$site <- "Oudekraal" 
oude_autumn_mean <- oude_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_autumn_mean$season <- "Autumn" 
oude_autumn_mean$site <- "Oudekraal"

oude_winter <- tidync("OceanParcels/chapter_4_output/oudekraal_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_winter$season <- "Winter" 
oude_winter$site <- "Oudekraal" 
oude_wintermean <- oude_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_winter_mean$season <- "Winter" 
oude_winter_mean$site <- "Oudekraal"

oude_spring <- tidync("OceanParcels/chapter_4_output/oudekraal_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_spring$season <- "Spring" 
oude_spring$site <- "Oudekraal" 
oude_spring <- scar_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_spring_mean$season <- "Spring" 
oude_spring_mean$site <- "Oudekraal"

@@
